%-------------------------
% Resume in Latex
% Author : Tyler Johnson
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

% ✅ BULLETS ONLY FOR PROJECTS & EXPERIENCE
\newcommand{\resumeItemListStart}{\begin{itemize}[label={\tiny$\bullet$},leftmargin=0.3in]}

\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Tyler Johnson} \\ \vspace{1pt}
    \href{mailto:tylerjjohnson0502@gmail.com}{\underline{tylerjjohnson0502@gmail.com}} $|$
    \href{https://linkedin.com/in/tyler-jjohnson}{\underline{linkedin.com/in/tyler-jjohnson}} $|$
    \href{https://github.com/tyljj}{\underline{github.com/tyljj}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{
\textbf{Computer Engineering graduate} specializing in embedded firmware and hardware-integrated systems. Experience with STM32 and ESP32 platforms, real-time sensor interfaces, and low-level debugging using oscilloscopes and logic analyzers. Proven ability to deliver documented, reliable automation solutions in safety-critical environments.
}



%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of St. Thomas}{Saint Paul, MN}
    {Bachelor of Computer Engineering}{Sep. 2021 -- May 2025}
\resumeSubHeadingListEnd



%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Java, Python, C, HTML/CSS, R, Verilog, Assembly} \\
    \textbf{Software \& Tools}{: Keil µVision, Visual Studio, Git/GitLab, Postman, Vivado} \\
    \textbf{Protocols}{: UART, SPI, I2C, Wi-Fi, Bluetooth} \\
    \textbf{Hardware \& Debugging}{: Oscilloscopes, logic analyzers, DMMs, soldering, board-level troubleshooting}
  }}
\end{itemize}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Robotic Arm FTIR Cleaning Automation} $|$ \emph{Python, Embedded Sensors}}{}
  \resumeItemListStart
    \resumeItem{Developed modular control software coordinating robotic motion, safety interlocks, and sensor feedback for a repeatable FTIR cleaning process.}
    \resumeItem{Implemented multi-threaded logic using event flags to handle door sensors and break-beam safety systems.}
    \resumeItem{Authored technical documentation covering system architecture, interfaces, and validation procedures.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Gas-Detecting Autonomous Robot} $|$ \emph{STM32 Embedded Firmware}}{}
  \resumeItemListStart
    \resumeItem{Programmed embedded firmware for real-time gas sensing, navigation decisions, and control logic.}
    \resumeItem{Debugged UART and I2C communication using oscilloscopes and logic analyzers.}
    \resumeItem{Performed iterative validation to verify sensor accuracy, timing stability, and system behavior.}
    \resumeItem{Structured firmware to support maintainability and repeatable testing.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{IoT Temperature Monitoring System} $|$ \emph{Distributed Embedded System}}{}
  \resumeItemListStart
    \resumeItem{Designed a multi-node embedded system using STM32 and Raspberry Pi platforms.}
    \resumeItem{Implemented structured data communication and logging for real-time monitoring.}
    \resumeItem{Documented system architecture, interfaces, and validation results for team review.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Papa Tronnio's Pizza}{Prescott, WI}
  {Restaurant Manager}{January 2022 -- January 2025}
  \resumeItemListStart
    \resumeItem{Led daily operations while supervising staff in a fast-paced environment.}
    \resumeItem{Maintained consistent processes, documentation, and quality standards.}
    \resumeItem{Communicated clearly with customers, employees, and ownership to resolve issues.}
    \resumeItem{Managed reporting, workflow organization, and accountability.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
